Mean Estimation from One-bit Measurements

### 2017-10-06 Slides/OneBit_Allerton_slides_V2.tex
final version of presentation

\begin{frame}
\frametitle{Related Work}
\begin{itemize} 
\pause
\item Estimation via compressed information [Han '87], [Zhang \& Berger '88] (centralized)
\pause
\item Estimation from multiple machines subject to a bit constraint [Zhang, Duchi, Jordan, Wainwright '13] (distributed / adaptive)
\pause
\item Distributed hypothesis testing under quantization [Tsitsiklis '88] (distributed)
\pause
\item Remote multiterminal source coding (CEO) [Berger, Zhang, Wiswanathan '96], [Oohama '97] (distributed)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Consistency}
Q: in what setting consistent estimation is possible? \\
\bigskip
\pause
A: all ! 
\pause
\bigskip
\textbf{Proof:}
\[
M_i = \mathbf 1(X_i>0),\quad i=1,\ldots,n
\]
(distributed setting)
\pause
\[
\frac{1}{n}\sum_{i=1}^n M_i \rightarrow \Prob\left(X>0 \right) = \Phi\left(\thetac / \sigma \right)
\]
\end{frame}

@@

\subsection{Preliminary}

\begin{frame}
\frametitle{Efficiency}
\textbf{Definition:} \emph{asymptotic relative efficiency (ARE)}:
\[
\mathrm{ARE}(\widehat{\theta}_n) \triangleq \lim_{n\rightarrow \infty} \mathbb E \left[ \left(\widehat{\theta}_n-\theta \right)^2 \right] / \left(\sigma^2 / n \right)
\]
(relative to minimax risk without bit constraint)
%SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
\bigskip

\pause
\begin{prop} ARE under centralized encoding is $1$
\end{prop}
\pause
\textbf{Proof:}
\[
\mathbb E \left( \theta- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \theta- \bar{\theta} \right)^2}^{\sigma^2/n} + \underbrace{\mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2}_{O(2^{-2n})}
\]

@@

%\node[int1, right of = enc2, node distance = 6cm, scale = 0.75] (est) {Est};
\draw[->,line width = 2pt] (enc1) -- node[above, xshift = 0cm, rotate = -15] (mes1) {one bit} (est);   
\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm, rotate = 12] (mes2) {one bit} (est);   
\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\thetac}_j$};
\draw[->, line width=2pt] (est) -- (dest);
\end{tikzpicture}
\end{center}
\begin{itemize}
\item $X_{1},\ldots,X_{n} \overset{\mathrm{i.i.d}}{\sim}\mathcal N(\theta,\sigma^2)$
\pause
\item Replicate $k$ times: $\thetac_1,\ldots,\thetac_k \overset{\iid}{\sim} \mathcal N(0,\sigma_0^2)$ 
\pause
\item Block encode $X_{j,1},\ldots,X_{j,n}$ using $k$ bits, $j=1,\ldots,k$
\pause
\item $D_{CEO} = \underset{k,\widehat{\theta}}{\inf} \frac{1}{k} \sum_{j=1}^k \mathbb E \left( \theta_j - \widehat{\theta}_j\right)^2$
\end{itemize}
%SAY: lower bound to our setting
\end{frame}

@@

\section{Adaptive Encoding} 
\begin{frame}
\frametitle{Three Encoding Scenarios}

@@

\begin{itemize}
\item Distributed: $M_i = f_i(X_i)$  \hfill{ARE $\geq 4/3$}
\visible<2->{
\item {Centralized}: $M^n = f(X_1,\ldots,X_n)$ \hfill{ARE $=1$} }
\visible<3->{
\item Next: {\color{red} adaptive / sequential: $M_i = f_i(X_i,M^{i-1})$ \hfill{ARE$=\pi/2$} }  }
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Achievability}
\framesubtitle{existence of an estimator with ARE $= \pi/2$}

\begin{itemize}
\item[(i)] For $X \sim \mathcal{N}(\theta,\sigma^2)$, $\mathsf{med}(X) = \theta$ 
\pause
\item[(ii)] $\mathsf{med}(X) = \underset{m}{ \mathrm{argmin~}} \mathbb E \left|X-m \right|$
\pause
\item[(iii)] Stochastic gradient descent on $\mathbb E \left| X-\theta \right|$:
\[
\theta_n = \theta_{n-1} + \gamma_n \sgn(X_n - \theta_n)
\]
\[
\widehat{\theta}_n = \frac{1}{n} \sum_{i=1}^n \theta_i 
\]
\end{itemize}
\bigskip
\pause
From [Polyak \& Juditsky '92] (under conditions on $(\gamma_n)$): 
\[
\sqrt{n}(\theta- \widehat{\theta}_n) \rightarrow \mathcal N\left(0, \sigma^2 \pi /2 \right)
\]
(MSE convergence follows from [Polyak '90]) 
\end{frame}
%picture

@@

\begin{frame}
\frametitle{Converse}
\framesubtitle{ARE $\geq \pi/2$}
Let $\pi(\theta)$ be a prior on $\Theta$. The van-Trees inequality (e.g. [Tsybakov '08]) implies
\[
\mathbb E \left(\theta - \widehat{\theta} \right)^2 \geq \frac{1}{\mathbb E I_\theta(M^n) + I_\pi} \geq \frac{1}{\sum_{i=1}^n I_\theta(M_i|M^{i-1}) + I_\pi} 
\]
$I_\pi$ is the location Fisher information with w.r.t. $\pi(\theta)$ \\

\begin{lem}[K. \& Duchi '17]
\[
I_\theta(M_i|M^{i-1}) \leq \frac{2}{\pi\sigma^2}
\]
\end{lem}
\textbf{Proof}: \\
Stein identity implies that portion maximizing the information is a threshold: $M_i^{-1}(1) = (\theta,\infty)$  \\
The rest follows by induction over number of portions
%SAY: the rest follows by induction over number 
\end{frame}

@@

\begin{frame}
\frametitle{Distributed Encoding}
\framesubtitle{Threshold Detection}
We consider only messages of the form
\[
M_i = \sgn(X_i - t_i),\quad i=1,\ldots,n
\]
\begin{center}
\pause
\begin{tikzpicture}
\node[coordinate] at(0,0) (ti) {};
\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_i$} +(0,-0.2);
\draw[<-,line width = 1pt] (-3,0) -- node[above] {$M_i=-1$} (ti);
\draw[->,line width = 2pt] (ti) -- node[above] {$M_i=1$} (6,0);
\end{tikzpicture}
\end{center}
Assume:
\[
\lambda_n([a,b]) = \frac{1}{n} \mathsf{card}\left( [a,b]  \cap \left\{t_i \right\} \right)
\]
converges weakly to a probability distribution $\lambda$
\\
\bigskip
\pause
\textbf{Example:} $t_1,\ldots,t_n$ drawn i.i.d. from a distribution $\lambda$ on $\mathbb R$

@@

\begin{frame}
\frametitle{Main Results (distributed encoding)}

\begin{theorem}
\begin{itemize}
\item[(i)] The Maximum likelihood estimator $\widehat{\theta}_{ML}$  satisfies
\[
\sqrt{n}(\theta - \widehat{\theta}_{ML}) \rightarrow \mathcal N\left(0,\sigma^2/K_\lambda(\theta) \right)
\]
where:
\begin{align*}
K_\lambda(\theta) & = \int_{\mathbb R} \eta\left( \frac{t-\theta}{\sigma}\right) \lambda(dt) \\
\eta(x) & = \frac{\phi^2(x)}{\Phi(x)\Phi(-x)}
\end{align*}
% The weight function in the probit analysis
\pause
\item[(ii)] For any estimator $\widehat{\theta}(M_1,\ldots,M_n)$:
\[
\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left(\widehat{\theta} - \tau \right)^2 \geq \sigma^2/K_\lambda(\theta),
\]

@@

\begin{frame}
\frametitle{Interpretations}
\begin{itemize}
\pause
\item MLE is local asymptotically minimax 
\pause
\item ARE of MLE is $1/K_{\lambda}(\theta)$ -- 
only depends on asymptotic threshold density $\lambda$
\pause
\item  
\[
\mathrm{ARE} = \frac{1}{K_{\lambda}(\theta)}  = \frac{\sigma^2}{\int \eta \left( \frac{t-\theta}{\sigma}\right) \lambda(dt)}
> \pi / 2
\]
(equality iff $\lambda = \delta_{\theta}$)
%SAY: cannot be as good as sequential thresholds
%\item Threshold density $\lambda$ that maximizes
\pause
\item Minimax $\lambda$ can be found using a convex program -- minimax ARE  depends on radius of $\Theta$
%ARE depends on size of parameter space $\Theta$ 
%\begin{center}
%\begin{tikzpicture}
%\node at (0,0)  {\includegraphics[scale=0.3]{k_vs_b2}};
%\node at (0,-1.7) {$r$};
%\node[rotate = 90] at (-2.3,0) {$1/K_{\lambda^\star}$};
%\end{tikzpicture}
%
%Minimax ARE vs radius $r$ of parameter space
%\end{center}

@@

\begin{frame}
\frametitle{Summary}
\begin{itemize}
\pause
\item Centralized encoding: ARE$=1$
\pause
\item Adaptive:
\begin{itemize}
\item ARE is $\pi/2$ (regardless of radius of $\Theta$)
\pause
\item $\sim 1.57$ more samples are required due to 1-bit constraints
\end{itemize}
\pause
%\pause
%\item One-step optimal one-bit message is a threshold detector
\bigskip
\item Distributed threshold detection:
\begin{itemize}
\item ARE of MLE characterized by density of threshold values 
\pause
\item MLE is local asymptotically optimal 
\pause
\item minimax ARE depends on radius of $\Theta$
\end{itemize}
%\item Minimax ARE of MLE depends on size of parameter space
\end{itemize}

@@

\begin{frame}
\frametitle{Minimax threshold density}

@@

\begin{frame}
\frametitle{Minimax $\lambda$}
\begin{center}
support of optimal threshold density $\lambda^\star$
\vspace{10pt}
\hspace{-27pt}
\begin{tikzpicture}
\node[int] (b1) at (0,0)  {\includegraphics[scale=0.23]{minimax_b_only1}};
\node[int] (b2) at (3.9,0)  {\includegraphics[scale=0.23]{minimax_b_only2}};
\node[int] (b3) at (7.8,0)  {\includegraphics[scale=0.23]{minimax_b_only5}};
\node[int] (b4) at (0,-3)  {\includegraphics[scale=0.23]{minimax_b_only10}};
\node[int] (b5) at (3.9,-3)  {\includegraphics[scale=0.23]{minimax_b_only50}}; 
\node[int] (b6) at (7.8,-3)  {\includegraphics[scale=0.23]{minimax_b_only100}}; 
\end{tikzpicture}
\end{center}
\[
K^\star = \inf_{\theta} K^\star(\theta) = \inf_\theta \int \eta(t-\theta) \lambda^\star(dt)
\]
\end{frame}

\begin{frame}
\frametitle{Minimax $\lambda$}
\begin{center}
Minimax ARE vs size of parameter space %$\Theta= (-\sigma b, \sigma,b)$

@@

\node at (0,0)  {\includegraphics[scale=0.35]{K_vs_b}};
\node at (0,-2) {$2b$};
\node[rotate = 90] at (-2.7,0) {$\frac{1}{2b} \times 1/K^\star$};
\end{tikzpicture}
\end{center}
\begin{itemize}
\item ARE increases with size of parameter space
\end{itemize}

\begin{frame}
\frametitle{One-step Optimal Scheme}
Initialization: $P_0(t) = \pi(\theta)$ \\
Repeat for $n \geq 1$:
\begin{itemize}
\item[(i)] $P_n(t) = \Prob(\theta = t|M^n) = \alpha_n P_{n-1}(t) \Phi \left(M_n \frac{t-\tau_{n-1}}{\sigma} \right)$ 
\item[(ii)] $\widehat{\theta} = \mathbb E[\theta | M^n] = \int t P_n(t)dt $ 
\item[(iii)] Find $\tau_n$ from 
\[
\tau_n = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau t P_n(t)dt }{\int_{-\infty}^\tau P_n(t)dt}  + \frac{ \int_{\tau}^\infty t P_n(t)dt}{\int_{\tau}^\infty P_n(t)dt} \right)
\]
\item[(iv)] $M_{n+1} = \sgn(X_{n+1}-\tau_n)$
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Numerical Example}
\begin{center}
Normalized empirical risk versus number of samples $n$ \\
(1000 Monte Carlo experiments)
\begin{tikzpicture}
\node at (0,0) {\includegraphics[scale=0.5]{one_bit_adaptive}};
%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
\node[rotate = 90, scale = 1] at (-5,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
\node[scale = 1] at (0,-3) {$n$};
%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
\end{tikzpicture}
$\theta \sim \unif(-3,3)$
\end{center}
\end{frame}

>>>>

\begin{frame}
\frametitle{Related Work}
\begin{itemize} 
\pause
\item Estimation via compressed information [Han '87], [Zhang \& Berger '88] (centralized)
\pause
\item Estimation from multiple machines subject to a bit constraint [Zhang, Duchi, Jordan, Wainwright '13] (distributed / adaptive)
\pause
\item Remote multiterminal source coding (CEO) [Berger, Zhang, Wiswanathan '96], [Oohama '97] (distributed)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Consistency}
Q: in what setting consistent estimation is possible? \\
\bigskip
\pause
A: all ! 
\pause
\bigskip
\textbf{Proof:}
\[
M_i = \mathbf 1(X_i>0),\quad i=1,\ldots,n
\]
(distributed setting)
\pause
\[
\frac{1}{n}\sum_{i=1}^n M_i \rightarrow \Prob\left(X>0 \right) = \Phi\left(\thetac / \sigma \right)
\]
\pause
\[
\sigma \Phi^{-1}\left( \frac{1}{n}\sum_{i=1}^n M_i  \right) \rightarrow \thetac
\]
\end{frame}

@@

\subsection{Preliminaries}

\begin{frame}
\frametitle{Efficiency}
\textbf{Definition:} \emph{asymptotic relative efficiency (ARE)}:
\[
\mathrm{ARE}(\widehat{\theta}_n) \triangleq \lim_{n\rightarrow \infty} \mathbb E \left[ \left(\widehat{\theta}_n-\thetac \right)^2 \right] / \left(\sigma^2 / n \right)
\]
(relative to sample mean $\bar{\theta}$)
%SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
\bigskip

\pause
\begin{prop} ARE under centralized encoding is $1$
\end{prop}
\pause
\textbf{Proof:}
\[
\mathbb E \left( \thetac- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \thetac- \bar{\theta} \right)^2}^{\sigma^2/n} + \mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2
\]
\end{frame}

\begin{frame}
\frametitle{Efficiency}
\textbf{Definition:} \emph{asymptotic relative efficiency (ARE)}:
\[
\mathrm{ARE}(\widehat{\theta}_n) \triangleq \lim_{n\rightarrow \infty} \mathbb E \left[ \left(\widehat{\theta}_n-\theta \right)^2 \right] / \left(\sigma^2 / n \right)
\]
(relative to sample mean $\bar{\theta}$)
%SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
\bigskip

\begin{prop} ARE under centralized encoding is $1$
\end{prop}
\textbf{Proof:}
\[
\mathbb E \left( \theta- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \theta- \bar{\theta} \right)^2}^{\sigma^2/n} + \underbrace{\mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2}_{O(2^{-2n})}
\]
\end{frame}

@@

%\node[int1, right of = enc2, node distance = 6cm, scale = 0.75] (est) {Est};
\draw[->,line width = 2pt] (enc1) -- node[above, xshift = 0cm, rotate = -15] (mes1) {one bit} (est);   
\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm, rotate = 12] (mes2) {one bit} (est);   
\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\thetac}_j$};
\draw[->, line width=2pt] (est) -- (dest);
\end{tikzpicture}
\end{center}
\begin{itemize}
\item $X_{1},\ldots,X_{n} \overset{\mathrm{i.i.d}}{\sim}\mathcal N(\thetac,\sigma^2)$
\pause
\item Replicate $k$ times: 
\begin{itemize}
\item  $\thetac_1,\ldots,\thetac_k \overset{\iid}{\sim} \mathcal N(0,\sigma_0^2)$ 
\item $\thetac_j \rightarrow X_{j,1},\ldots,X_{j,n}$
\end{itemize}
\pause
\item Encoder $i$ block encodes $X_{1,i},\ldots,X_{k,i}$ using $k$ bits
\pause
\item $D_{CEO} = \underset{k}{\inf} \frac{1}{k} \sum_{j=1}^k \mathbb E \left( \theta_j - \widehat{\theta}_j\right)^2$
\end{itemize}
%SAY: lower bound to our setting
\end{frame}

@@

\section{Adaptive Encoding}

@@

\begin{itemize}
\item Distributed: $M_i = f_i(X_i)$  \hfill{ARE $\geq 4/3$}
\visible<2->{
\item {Centralized}: $M^n = f(X_1,\ldots,X_n)$ \hfill{ARE $=1$} }
\visible<3->{
\item Next: {\color{red} adaptive: $M_i = f_i(X_i,M^{i-1})$ \hfill{ARE$=\pi/2$} }  }
\end{itemize}
\end{frame}

\subsection{Main Results}

@@

\begin{frame}
\frametitle{Achievability}
\framesubtitle{existence of an estimator with ARE $= \pi/2$}
\pause
\begin{itemize}
\item[(i)] For $X \sim \mathcal{N}(\theta,\sigma^2)$, $\mathsf{med}(X) = \theta$ 
\pause
\item[(ii)] $\mathsf{med}(X) = \underset{m}{ \mathrm{argmin~}} \mathbb E \left|X-m \right|$
\pause
\item[(iii)] Stochastic gradient descent on $\mathbb E \left| X-\theta \right|$:
\pause
\begin{flushright}
\begin{tikzpicture}
\node[coordinate] at(0,0) (ti) {};
\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $\theta$} +(0,-0.2);
\draw[<-,line width = 2pt] (-1.5,0) -- node[above] {$-1$} (ti);
\draw[->,line width = 2pt] (ti) -- node[above] {$1$} (1.5,0);
\draw (-1.3,1.5) -- (ti) -- (1.3,1.5);
\end{tikzpicture}
\end{flushright}
\[
\theta_n = \theta_{n-1} + \gamma_n \sgn(X_n - \theta_n)
\]
\[
\widehat{\theta}_n = \frac{1}{n} \sum_{i=1}^n \theta_i 
\]
\end{itemize}
\bigskip
\pause
From [Polyak \& Juditsky '92] (under conditions on $(\gamma_n)$): 
\[
\sqrt{n}(\theta- \widehat{\theta}_n) \rightarrow \mathcal N\left(0, \sigma^2 \pi /2 \right)
\]
\end{frame}
%picture

@@

\begin{frame}
\frametitle{Converse}
\framesubtitle{ARE $\geq \pi/2$}
The van-Trees inequality (e.g. [Tsybakov '08]) implies
\[
\mathbb E \left(\theta - \widehat{\theta} \right)^2 \geq \frac{1}{ I_\theta(M^n) + c} = \frac{1}{\sum_{i=1}^n I_\theta(M_i|M^{i-1}) + c} 
\]
\pause
\begin{lem}[K. \& Duchi '17]
\[
I_\theta(M_i|M^{i-1}) \leq \frac{2}{\pi\sigma^2}
\]
\end{lem}
\pause
\textbf{Proof}: \\
Stein's identity implies that detection region maximizing the information is a threshold: $M_i^{-1}(1) = (\theta,\infty)$ 
%SAY: the rest follows by induction over number 
\end{frame}

@@

\subsection{Threshold Detection}

\begin{frame}
\frametitle{Distributed Encoding}
\framesubtitle{Threshold Detection}
We consider only messages of the form
\[
M_i = \sgn(X_i - t_i),\quad i=1,\ldots,n
\]
\pause
\begin{center}
\begin{tikzpicture}
\draw[<->,line width = 1pt] (-3,0) node[left] {$\cdots$} -- (3,0) node[right] {$\cdots$};
\node[coordinate] at(0,0) (ti) {};
%\draw[<-,line width = 1pt] (-3,0) -- node[above] (ti);
%\draw[->,line width = 1pt] (ti) -- node[above]  (6,0);
\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_1$} +(0,-0.2);
\pause
\node[coordinate] at(2,0) (tj) {};
\draw[color = blue, line width = 1.5pt] (tj)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_2$} +(0,-0.2);
\pause
\node[coordinate] at(-1,0) (tk) {};
\draw[color = green, line width = 1.5pt] (tk)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_3$} +(0,-0.2);
\end{tikzpicture}
\end{center}
%Assume:
%\[
%\lambda_n([a,b]) = \frac{1}{n} \mathsf{card}\left( [a,b]  \cap \left\{t_i \right\} \right)
%\]
%converges weakly to a probability distribution $\lambda$
%\\
%\bigskip
%\pause
%\textbf{Example:} $t_1,\ldots,t_n$ drawn i.i.d. from a distribution $\lambda$ on $\mathbb R$ 
\end{frame}

\begin{frame}
\frametitle{Distributed Encoding}
\framesubtitle{Threshold Detection}
We consider only messages of the form
\[
M_i = \sgn(X_i - t_i),\quad i=1,\ldots,n
\]
\begin{center}
\begin{tikzpicture}
\draw[<->,line width = 1pt] (-3,0) node[left] {$\cdots$} -- (3,0) node[right] {$\cdots$};
\node[coordinate] at(0,0) (ti) {};
%\draw[<-,line width = 1pt] (-3,0) -- node[above] (ti);
%\draw[->,line width = 1pt] (ti) -- node[above]  (6,0);
\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_1$} +(0,-0.2);
\node[coordinate] at(2,0) (tj) {};
\draw[color = blue, line width = 1.5pt] (tj)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_2$} +(0,-0.2);
\node[coordinate] at(-1,0) (tk) {};
\draw[color = green, line width = 1.5pt] (tk)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_3$} +(0,-0.2);
\end{tikzpicture}
\end{center}
Assume:
\[
\lambda_n([a,b]) = \frac{1}{n} \mathsf{card}\left( [a,b]  \cap \left\{t_i \right\} \right)
\]
converges weakly to a probability distribution $\lambda$
\\
\bigskip
\pause
\textbf{Example:} $t_1,\ldots,t_n$ drawn i.i.d. from a distribution $\lambda$ on $\mathbb R$

@@

\begin{frame}
\frametitle{Main Results (distributed encoding)}
\pause
\begin{theorem}
\begin{itemize}
\item[(i)] The Maximum likelihood estimator $\widehat{\theta}_{ML}$  satisfies
\[
\sqrt{n}(\theta - \widehat{\theta}_{ML}) \rightarrow \mathcal N\left(0,\sigma^2/K_\lambda(\theta) \right)
\]
where:
\begin{align*}
K_\lambda(\theta) & = \int_{\mathbb R} \eta\left( \frac{t-\theta}{\sigma}\right) \lambda(dt) \\
\eta(x) & = \frac{\phi^2(x)}{\Phi(x)\Phi(-x)}
\end{align*}
% The weight function in the probit analysis
\pause
\item[(ii)] For any estimator $\widehat{\theta}(M_1,\ldots,M_n)$:
\[
\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left(\widehat{\theta} - \tau \right)^2 \geq \sigma^2/K_\lambda(\theta),
\]

@@

\begin{frame}
\frametitle{Interpretations}
\begin{itemize}
\pause
\item MLE is local asymptotically minimax 
\pause
\item  ARE of MLE is $1/K_{\lambda}(\theta)$ -- 
only depends on asymptotic threshold density $\lambda$
\pause
\item
\[
\mathrm{ARE} = \frac{1}{K_{\lambda}(\theta)}  = \frac{\sigma^2}{\int \eta \left( \frac{t-\theta}{\sigma}\right) \lambda(dt)}
> \pi / 2
\]
(equality iff $\lambda = \delta_{\theta}$)

%SAY: cannot be as good as sequential thresholds
%\item Threshold density $\lambda$ that maximizes
%\pause
%\item Minimax $\lambda$ can be found using a convex program -- minimax ARE  depends on radius of $\Theta$
%ARE depends on size of parameter space $\Theta$ 
%\begin{center}
%\begin{tikzpicture}
%\node at (0,0)  {\includegraphics[scale=0.3]{k_vs_b2}};
%\node at (0,-1.7) {$r$};
%\node[rotate = 90] at (-2.3,0) {$1/K_{\lambda^\star}$};
%\end{tikzpicture}
%
%Minimax ARE vs radius $r$ of parameter space
%\end{center}

@@

\begin{frame}
\frametitle{Summary}
\begin{itemize}
\pause
\item Centralized encoding: ARE$=1$
\pause
\item Adaptive:
\begin{itemize}
\item ARE is $\pi/2$ % (regardless of radius of $\Theta$)
\pause
\item $\sim 1.57$ more samples are required due to 1-bit constraints
\end{itemize}
\pause
%\pause
%\item One-step optimal one-bit message is a threshold detector
\bigskip
\item Distributed threshold detection:
\begin{itemize}
\item ARE of MLE characterized by density of threshold values 
\pause
\item MLE is local asymptotically optimal 
\pause
%\item minimax ARE depends on radius of $\Theta$
\end{itemize}
%\item Minimax ARE of MLE depends on size of parameter space
\end{itemize}

@@

\begin{frame}[noframenumbering]
\frametitle{Minimax threshold density}

@@

\begin{frame}[noframenumbering]
\frametitle{Minimax $\lambda$}
\begin{center}
support of optimal threshold density $\lambda^\star$
\vspace{10pt}
\hspace{-27pt}
\begin{tikzpicture}
\node[int] (b1) at (0,0)  {\includegraphics[scale=0.23]{minimax_b_only1}};
\node[int] (b2) at (3.9,0)  {\includegraphics[scale=0.23]{minimax_b_only2}};
\node[int] (b3) at (7.8,0)  {\includegraphics[scale=0.23]{minimax_b_only5}};
\node[int] (b4) at (0,-3)  {\includegraphics[scale=0.23]{minimax_b_only10}};
\node[int] (b5) at (3.9,-3)  {\includegraphics[scale=0.23]{minimax_b_only50}}; 
\node[int] (b6) at (7.8,-3)  {\includegraphics[scale=0.23]{minimax_b_only100}}; 
\end{tikzpicture}
\end{center}
\[
K^\star = \inf_{\theta} K^\star(\theta) = \inf_\theta \int \eta(t-\theta) \lambda^\star(dt)
\]
\end{frame}

\begin{frame}[noframenumbering]
\frametitle{Minimax $\lambda$}
\begin{center}
Minimax ARE vs size of parameter space %$\Theta= (-\sigma b, \sigma,b)$

@@

\node at (0,0)  {\includegraphics[scale=0.35]{K_vs_b}};
\node at (0,-2) {$2b$};
\node[rotate = 90] at (-2.7,0) {$\frac{1}{2b} \times 1/K^\star$};
\end{tikzpicture}
\end{center}
\begin{itemize}
\item ARE increases with size of parameter space
\end{itemize}
\end{frame}

\begin{frame}[noframenumbering]
\frametitle{One-step Optimal Scheme}
Initialization: $P_0(t) = \pi(\theta)$ \\
Repeat for $n \geq 1$:
\begin{itemize}
\item[(i)] $P_n(t) = \Prob(\theta = t|M^n) = \alpha_n P_{n-1}(t) \Phi \left(M_n \frac{t-\tau_{n-1}}{\sigma} \right)$ 
\item[(ii)] $\widehat{\theta} = \mathbb E[\theta | M^n] = \int t P_n(t)dt $ 
\item[(iii)] Find $\tau_n$ from 
\[
\tau_n = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau t P_n(t)dt }{\int_{-\infty}^\tau P_n(t)dt}  + \frac{ \int_{\tau}^\infty t P_n(t)dt}{\int_{\tau}^\infty P_n(t)dt} \right)
\]
\item[(iv)] $M_{n+1} = \sgn(X_{n+1}-\tau_n)$
\end{itemize}
\end{frame}

\begin{frame}[noframenumbering]
\frametitle{Numerical Example}
\begin{center}
Normalized empirical risk versus number of samples $n$ \\
(1000 Monte Carlo experiments)
\begin{tikzpicture}
\node at (0,0) {\includegraphics[scale=0.5]{one_bit_adaptive}};
%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
\node[rotate = 90, scale = 1] at (-5,0) {$n \ mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
\node[scale = 1] at (0,-3) {$n$};
%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
\end{tikzpicture}
$\theta \sim \unif(-3,3)$
\end{center}
\end{frame}
